---
title: "San Francisco Airbnb Listing"
author: "Amy Johnson"
date: "3/7/2020"
output: 
  html_document: 
    keep_md: yes
---

## I chose San Francisco as the final project because it's one of my farviorte city in the states  


#packages needed
library(GISTools)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(jsonlite)
library(rgdal)
library(sf)
library(sp)
library(tmap)



```{r load dataset}
SanFran.Airbnblistings <- read.csv("~/Graduate_School_Rockhurst/BIA_6313_GIS_SpringA2020/Final Project/San Francisco Airbnb listings.csv", header = TRUE)

#change the first row to be the header
SanFran.Airbnb <- SanFran.Airbnblistings[-1,]
```



```{r select room type}
#filter only to private room
room_type <- data.frame(unique(SanFran.Airbnb$room_type))
library(tidyverse)
Private_room <- SanFran.Airbnb %>% filter(room_type == "Private room")
SanFran.Airbnb <- filter(Private_room)
#delete columns that has no vlaue
SanFran.Airbnb <- SanFran.Airbnb[,-5]
#delete Hotels
SanFran.Airbnb <- SanFran.Airbnb[c(-2396,-2397,-2398,-2399,-2400,-2378,-2379,-2380,-2381),]
```


```{r convert from unprojected to projected}
#convert a CSV file into a spatial object
library(rgdal)
library(sf)
SF.Airbnb.Pvt <- SanFran.Airbnb
coordinates(SF.Airbnb.Pvt)= ~longitude+latitude
class(SF.Airbnb.Pvt)
```

```{r set CRS}
#setting the CRS WG84
proj4string(SF.Airbnb.Pvt) <- CRS("+init=EPSG:4326")
SF.Airbnb.Pvt@proj4string
```


```{r plot listngs by private room}
plot(SF.Airbnb.Pvt)
```
```{r import San Francisco shapefile}
library(rgdal)
SanFran <- readOGR("~/Graduate_School_Rockhurst/BIA_6313_GIS_SpringA2020/Final Project/SF Find Neighborhoods")

class(SanFran)

head(SanFran@data,20)

plot(SanFran)
```
```{r sf object to see neighborhood name}
#To see San Francisco by neighborhood color variance
library(sf)
SanFran_sf <- st_as_sf(SanFran)
class(SanFran_sf)
plot(SanFran_sf["name"])
```

```{r ensure CRS for both SanFran sp object}
SanFran@proj4string
#change CRS to match Airbnb date frame
proj4string(SanFran) <- CRS("+init=EPSG:4326")
SanFran@proj4string
```

```{r change airbnb data to sf object}
SF.Airbnb_sf <- st_as_sf(SF.Airbnb.Pvt)
class(SF.Airbnb_sf)
```

# Map all the listings by private room type  

```{r tmap}
library(tmap)
tm_shape(SanFran)+
  tm_polygons("white")+
  tm_shape(SF.Airbnb.Pvt)+
  tm_dots(size = 0.1, shape = 19, col = "red", alpha = 0.5)
```

```{r tmap1}
library(tmap)
tm_shape(SanFran_sf)+
  tm_fill("white")+
  tm_borders()+
  tm_shape(SF.Airbnb_sf)+
  tm_dots(size = 0.1, shape = 19, col = "red", alpha = 0.5)+
  tm_text("neighbourhood", size = 0.2)
 
  
#Too many neighbourhood hard to see the name of each neighbourhood
```

```{r mapview}
library(mapview)
mapview(SF.Airbnb.Pvt)
```

```{r turn off the interactive mode}
tmap_mode("plot")
```

#Spatial Proximity Polygons  

```{r proximity polygons}
require(deldir)
require(sp)
```

```{r Modified Carson Farmer code}
voronoipolygons = function(layer) {
  crds <- layer@coords
  z <- deldir(crds[,1], crds[,2])
  w <- tile.list(z)
  polys <- vector(mode='list', length=length(w))
  for (i in seq(along=polys)) {
    pcrds <- cbind(w[[i]]$x, w[[i]]$y)
    pcrds <- rbind(pcrds, pcrds[1,])
    polys[[i]] <- Polygons(list(Polygon(pcrds)),
                           ID=as.character(i))
  }
  SP <- SpatialPolygons(polys)
  voronoi <- SpatialPolygonsDataFrame(SP, 
                                      data=data.frame(x = seq(length(SP)),
                                                      row.names=sapply(slot(SP, 'polygons'), 
                                                                       function(x) slot(x, 'ID'))))
  proj4string(voronoi) <- CRS(proj4string(layer))
  return(voronoi)
}


library(gstat)
library(tmap)


SF.Airbnb.voro <- voronoipolygons(SF.Airbnb.Pvt)

tmap_mode('plot')
fpt <- tm_shape(SF.Airbnb.Pvt) + tm_dots(size=0.01)
fvr <- tm_shape(SF.Airbnb.voro) + tm_borders()
tmap_arrange(fpt,fvr)

library(gstat)
library(GISTools)
tmap_mode('view')
sh <- shading(breaks=c(15,30,45,60,75),cols=brewer.pal(6,'YlGn'))
tm_shape(SF.Airbnb.voro) + tm_fill("lightgrey", col = 'x', alpha=0.6, title='Airbnb Price')


```
# Inverse Distance Weight(IDW)  

```{r IDW}

library(maptools)
library(GISTools) 
library(gstat) # Set up the gstat package
# Define a sample grid then use it as a set of points 
# to estimate fulmar density via IDW, with alpha=1 (inverse relationship)
s.grid <- spsample(SF.Airbnb.voro,type='regular',n=10000)
idw.est <- gstat::idw(price~1,SF.Airbnb.Pvt,
                      newdata=s.grid,idp=1.0)

tmap_mode('view')
tm_shape(idw.est) + tm_dots(col='var1.pred',border.col=NA,alpha=0.7)
tmap_mode('view')
idw.grid <- SpatialPixelsDataFrame(idw.est,data.frame(idw.est)) 
tm_shape(idw.grid) + tm_raster(col='var1.pred',title='Price')
```


### What about when the idp (alpha) = 2.0  

```{r IDW alpha 2}
idw.est2 <- gstat::idw(price~1,SF.Airbnb.Pvt,
                       newdata=s.grid,idp=2.0)
idw.grid2 <- SpatialPixelsDataFrame(idw.est2,data.frame(idw.est2)) 
tmap_mode('view')
tm_shape(idw.grid2) +  tm_raster(col='var1.pred',title='Airbnb Price')

tmap_mode('plot')
idw1 <- tm_shape(idw.grid) +  tm_raster(col='var1.pred',title='Alpha = 1')
idw2 <- tm_shape(idw.grid2) +  tm_raster(col='var1.pred',title='Alpha = 2')
tmap_arrange(idw1,idw2)
```



### What about when the idp (alpha) = 3.0  

```{r IDW alpha 3}
idw.est3 <- gstat::idw(price~1,SF.Airbnb.Pvt,
                       newdata=s.grid,idp=3.0)
idw.grid3 <- SpatialPixelsDataFrame(idw.est3,data.frame(idw.est3)) 
tmap_mode('view')
tm_shape(idw.grid3) +  tm_raster(col='var1.pred',title='Airbnb Price')

tmap_mode('plot')
idw2 <- tm_shape(idw.grid2) +  tm_raster(col='var1.pred',title='Alpha = 2')
idw3 <- tm_shape(idw.grid3) +  tm_raster(col='var1.pred',title='Alpha = 3')
tmap_arrange(idw2,idw3)
```

### Alpha changed from 1, 2 and 3, it displays opposite what I was expecting. when alpha increase, the prediction is lower  


#Trend Surface Analysis  

```{r trend surface analysis} 
library(rgdal)
library(tmap)

SF.Airbnb.Pvt@bbox <- SF.Airbnb.voro@bbox

tm_shape(SF.Airbnb.voro) + tm_polygons() +
  tm_shape(SF.Airbnb.Pvt) +
  tm_dots(col="price", palette = "RdBu", auto.palette.mapping = FALSE,
          title="SF Airbnb Price \n", size=0.7) +
  tm_text("price", just="left", xmod=.5, size = 0.7) +
  tm_legend(legend.outside=TRUE)
```

```{r grid}

# Create an empty grid where n is the total number of cells
grd              <- as.data.frame(spsample(SF.Airbnb.Pvt, "regular", n=50000))
names(grd)       <- c("X", "Y")
coordinates(grd) <- c("X", "Y")
gridded(grd)     <- TRUE  # Create SpatialPixel object
fullgrid(grd)    <- TRUE  # Create SpatialGrid object

# Add P's projection information to the empty grid
proj4string(grd) <- proj4string(SF.Airbnb.Pvt)

# Define the 1st order polynomial equation
f.1 <- as.formula(price ~ X + Y) 

# Add X and Y to Houses
SF.Airbnb.Pvt$X <- coordinates(SF.Airbnb.Pvt)[,1]
SF.Airbnb.Pvt$Y <- coordinates(SF.Airbnb.Pvt)[,2]

# Run the regression model
lm.1 <- lm( f.1, data=SF.Airbnb.Pvt)

# Use the regression model output to interpolate the surface
dat.1st <- SpatialGridDataFrame(grd, data.frame(var1.pred = predict(lm.1, newdata=grd))) 

# Clip the interpolated raster to Texas
library(raster)
r   <- raster(dat.1st)
r.m <- mask(r, SF.Airbnb.voro)

# Plot the map
tm_shape(r.m) + 
  tm_raster(n=10, palette="RdBu", 
            title="SF Airbnb Price") +
  tm_shape(SF.Airbnb.Pvt) + tm_dots(size=0.2) +
  tm_legend(legend.outside=TRUE)


# Define the 2nd order polynomial equation
f.2 <- as.formula(price ~ X + Y + I(X*X)+I(Y*Y) + I(X*Y))

# Add X and Y to P
SF.Airbnb.Pvt$X <- coordinates(SF.Airbnb.Pvt)[,1]
SF.Airbnb.Pvt$Y <- coordinates(SF.Airbnb.Pvt)[,2]

# Run the regression model
lm.2 <- lm( f.2, data=SF.Airbnb.Pvt)

# Use the regression model output to interpolate the surface
dat.2nd <- SpatialGridDataFrame(grd, data.frame(var1.pred = predict(lm.2, newdata=grd))) 

# Clip the interpolated raster to Texas
r   <- raster(dat.2nd)
r.m <- mask(r, SF.Airbnb.voro)

# Plot the map
tm_shape(r.m) + 
  tm_raster(n=10, palette="RdBu",
            title="SF Airbnb Price") +
  tm_shape(SF.Airbnb.Pvt) + tm_dots(size=0.2) +
  tm_legend(legend.outside=TRUE)

```
### Comparing Linear and Polynomial models, I'd say the linear model seems present better prediction on the airbnb price based on locaitons  


#Ordinary Kriging  

```{r ordinary kriging}

#creating distance bands from 0 km to 250 km in step of 5km
require(gstat)
evgm <- variogram(price~1,SF.Airbnb.Pvt,
                  boundaries=seq(10,5000,l=51))
fvgm <- fit.variogram(evgm,vgm(10,"Mat",2500,1))#fit semivariogram using Matern function
plot(evgm,model=fvgm)


krig.est <- krige(price~1,SF.Airbnb.Pvt,newdata=s.grid,model=fvgm)
krig.grid <- SpatialPixelsDataFrame(krig.est,krig.est@data)

krig.map.est <- tm_shape(krig.grid) + 
  tm_raster(col='var1.pred',title='SF Airbnb Price',palette='Reds') + 
  tm_layout(legend.bg.color='white',legend.outside = TRUE)
var.levs <- c(0,3,6,9,12,Inf) 
krig.map.var <- tm_shape(krig.grid) + 
  tm_raster(col='var1.var',title='Estimate Variance',palette='Reds') + 
  tm_layout(legend.bg.color='white',legend.outside = TRUE)
tmap_arrange(krig.map.est,krig.map.var)
```
### Ordinary Kriging shows softer layers than linear models, they have very simlar predictions that closer to downtown is more expensive on renting airbnb  


# Multiple Linear Regression  

```{r structure of data frame}
str(SanFran.Airbnb)
```

```{r correltion plot}
library(corrplot)
corrs <- cor(SanFran.Airbnb[,c(9,10,11,14,15)])
corrplot(corrs, method = "number")
```

```{r spatial points}
head(SanFran.Airbnb)
plot(SanFran)


SanFran.Airbnb.spdf <- SpatialPointsDataFrame(SanFran.Airbnb[,6:7], SanFran.Airbnb)

plot(SanFran.Airbnb.spdf, add=T, pch=16)

# Not sure why I couldn't plot the airbnb data frame and the neighbourhood spaital polygons data frame, and I couldn't find a San Francisco city outline shapefile
```

```{r global mean and SD}
mean(SanFran.Airbnb.spdf$price)
sd(SanFran.Airbnb.spdf$price)
```


```{r local counterparts}
library(GWmodel)
localstats1 <- gwss(SanFran.Airbnb.spdf, vars = c("price"), bw=50000) #bandwidth is 50km

head(data.frame(localstats1$SDF))
```

```{r plot new}

library(RColorBrewer)
plot.new()
quick.map <- function(spdf,var,legend.title,main.title) {
  x <- spdf@data[,var]
  cut.vals <- pretty(x)
  x.cut <- cut(x,cut.vals)
  cut.levels <- levels(x.cut)
  cut.band <- match(x.cut,cut.levels)
  colors <- brewer.pal(length(cut.levels),'Reds')
  par(mar=c(1,1,1,1))
  plot(SanFran,col='grey85')
  title(main.title)
  plot(spdf,add=TRUE,col=colors[cut.band],pch=16)
  legend('topleft',cut.levels,col=colors,pch=16,bty='n',title=legend.title)
}

plot.new()
par(mfrow=c(1,2))
quick.map(localstats1$SDF, "price_LM",
          "US Dollar", "Geographically Weighted Mean")

quick.map(localstats1$SDF, "price_LSD",
          "US Dollar", "Local Standard Deviation")
```

````{r GWR regression}
## ----dogwr,cache=TRUE----------------------------------------------------
gwr.res <- gwr.basic(price~minimum_nights,
                     data=SanFran.Airbnb.spdf,bw=50000, kernel='gaussian')

## ----infogwr,size='tiny'-------------------------------------------------
gwr.res

```















